Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex

In relation to Bitcoin,researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p. 7), by either using a \textit{polarity classification} – classifying the language in tweets as either positive or negative (see Colianni et al., 2015) – or a \textit{lexicon based approach} – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017). Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further. inspired on analysis of the influence of twitter bullishness on the stock market by Mao et al. (2015), this paper applies the similar method to Bitcoin prices.\\

>>>>

In relation to Bitcoin,researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p. 7), by either using a \textit{polarity classification} – classifying the language in tweets as either positive or negative (see Colianni et al., 2015) – or a \textit{lexicon based approach} – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017). Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without futher analysing investors interests implied in the semantics. inspired on analysis of the influence of twitter bullishness on the stock market by Mao et al. (2015), this paper applies the similar method to Bitcoin prices.\\
